Stepwise Multiple Regressions

### 2021-02-04 Stepwise Multiple Regressions.Rmd
Factoring charge, particle source, and effect

  replace_na(list(size.category = 0, shape = "Not Reported", polymer = "Not Reported", life.stage = "Not Reported")) %>% 

@@

@@

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         charge, 
         particle.source,
         org_f,
         effect)

@@

#Fit the full model
Full_Model <- lm(effect ~., data = y)

@@

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

@@

#Fit the full model
Full_Model <- lm(effect ~., data = y)
```

@@

```{r, echo = FALSE}
summary(Full_Model)

@@

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         # size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

@@

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         # size_f, 
         size.length.um.used.for.conversions, 
         # shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

@@

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         charge, 
         particle.source,
         org_f,
         effect)

@@

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

@@

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         # size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

@@

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         # size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge, 
         # particle.source,
         org_f,
         effect)

@@

>>>>

  replace_na(list(size.category = 0, shape = "Not Reported", polymer = "Not Reported", life.stage = "Not Reported", charge = "Not Reported")) %>% 

@@

  mutate(charge_f = factor(case_when(charge == "negative" ~ "Negative",
                                     charge == "positive" ~ "Positive",
                                     charge == "Not Reported" ~ "Not Reported"))) %>%
  mutate(particle_source_f = factor(case_when(particle.source == "commercial" ~ "Commercial",
                                              particle.source == "lab" ~ "Lab",
                                              particle.source == "modified" ~ "Modified",
                                              particle.source == "N" ~ "Not Reported"))) %>% 

@@

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         charge_f, 
         particle_source_f,
         org_f,
         effect)

@@

#Fit the full model
Full_Model <- lm(effect_f ~., data = y)

@@

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge_f, 
         particle_source_f,
         org_f,
         effect_f)

@@

#Fit the full model
Full_Model <- lm(effect_f ~., data = y)

@@

@@

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         # size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge_f, 
         particle_source_f,
         org_f,
         effect_f)

@@

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         # size_f, 
         size.length.um.used.for.conversions, 
         # shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge_f, 
         particle_source_f,
         org_f,
         effect_f)

@@

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         charge_f, 
         particle_source_f,
         org_f,
         effect_f)

@@

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge_f, 
         particle_source_f,
         org_f,
         effect_f)

@@

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         # size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge_f, 
         particle_source_f,
         org_f,
         effect_f)

@@

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         # size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge_f, 
         # particle_source_f,
         org_f,
         effect_f)

@@

# GLM Exploration

Since a linear model does not seem to work well for this data set. I'm going to explore other distribution that may fit the data better.

```{r, echo = TRUE}

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         charge_f, 
         particle_source_f,
         org_f,
         effect_f)

str(aoc_setup_selected)
